---
title: "Project 4: Github Instructions -- Draft"
subtitle: "**Carnegie Mellon University**"
author: "Cyrus Daruwala, Xiong-Fei Du, Elias Roche, Kylee Santos"
date: "April 8, 2019"
output:
  html_document:
    theme: spacelab
    latex_engine: xelatex
    highlight: tango
    toc: true
    toc_depth: 3
    toc_float: true
mainfont: Lato
monofont: Ubuntu Mono
fontsize: 12pt
header-includes:
  - \usepackage{booktabs}
  - \usepackage{graphicx}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, out.width="90%", out.align="center")
library(tidyverse)

# USE THIS FUNCTION TO INSERT IMAGES!
p <- . %>% knitr::include_graphics()
```

# Background Information

TODO

---

# Setting up your Account

TODO

---

# Setting Up Git Repositories (Elias)

## `git init`

The `init` command creates an empty git repository -- a `.git` directory containing everything you need for version control in this repository.

#### Command Line

To initialize a repository from the command line:

1. Navigate to desired parent directory:
  - *This directory will contain the git repository.*

```bash
$ cd ~/cmu/76270/project4/
```

2. Create a directory for your repository:

```bash
$ mkdir github-instructions
```

3. Navigate to new directory:

```bash
$ cd github-instructions
```

4. Initialize the repository:

```bash
$ git init
```

#### GitHub

On `github.com`, the `init` command is run automatically when a repository is created. **Ensure that you are logged in before following these steps**:

1. Navigate to home page:
  - [`http://github.com`](http://github.com)

2. Click on the green **New** button on the top-left of the page:

```{r}
p("img/new-repository.png")
```

3. Enter a name for the repository:
   - *The name of the repository must be unique to your user -- that is, you cannot give two repositories the same name.*

4. Enter additional customizations:
  - _You can include an optional description to provide more information about the purpose of the repository._
  - _Repositories can be public (others can view and use your code), or private (only you and invited users can access the repository)._
  - _`README.md`, `.gitignore`, and `LICENSE` are typical files to include in a repository. They are addressed in a later section._

```{r}
p("img/create-repository.png")
```

5. Click on **Create Repository** to complete.
   - _The page will be redirected to the empty repositories home page._

6. Finally, set up the repository:
   - _You can create a new repository on the command line by running:_

```bash
$ echo "# github-instructions" >> README.md
$ git init
$ git add README.md
$ git commit -m "first commit"
$ git remote add origin git@github.com:reroche/github-instructions.git
$ git push -u origin master
```

  - _Or you can import an existing repository on your computer into this GitHub new repository by running:_

```bash
$ git remote add origin git@github.com:reroche/github-instructions.git
$ git push -u origin master
```

## `git clone`

The `clone` command creates a copy of a of a repository into a newly created directory.

All repositories on GitHub have a unique URL, in the format:

> `https://github.com/`_username_`/`_repository-name_`.git`

The repository for this instructions, for example, is available at [`https://github.com/reroche/github-instructions`](https://github.com/reroche/github-instructions).

#### Command Line

To clone a repository from the command line:

1. Navigate to the desired parent directory.

```bash
$ cd ~/cmu/76270/project4/
```

2. Clone the repository using its GitHub URL:
   - _The new repository will be in a directory with its original name (e.g._ `github-instructions`).

```bash
$ git clone https://github.com/reroche/github-instructions.git
```

#### GitHub

The online interface allows you to easily browse and copy repository URLs to clone via the command line.

To clone or download a repository from Github:

1. Navigate to the repository URL:

> `https://github.com/reactjs/reactjs.org`

2. Click the green "Clone or Download" button:

```{r}
p("img/clone-repository.png")
```

3. Copy the link and clone from the command line, or download ZIP file.

## Forking on GitHub

Forking is copying a repository that belongs to another user into your repositories, granting you ownership permissions over that repository.

Forking cannot be done via the command line.

To fork a repository on Github, simply click the "Fork" button on the top right of a repository's home page.

```{r}
p("img/fork-repository.png")
```

---

# Tools for Working Locally (Xiong-Fei)

## `git stash`

The `stash` command stores away your current local changes to revert to the previous commit. This is typically done when you have made changes to a repository that you have not committed, but want to undo.

### Command Line

Suppose you already have local changes in the repository that you want to stash away. To stash changes in command line:

1. Navigate to desired directory:

```bash
$ cd ~/cmu/76270/project4/github-instructions/
```

2. Clear uncommitted changes:

```bash
$ git stash
```

Now observe that your local changes are now gone. To bring these changes back, you can run the following command:

```bash
$ git stash pop
```

### GitHub TODO


## `git log`

The `log` command allows you to see the history of commits made to your repository.

### Command Line

To see the history of commits:

1. Navigate to desired directory:

```bash
$ cd ~/cmu/76270/project4/github-instructions/
```

2. To view commit history:

```bash
$ git log
```

Now observe the history of commits to this repository. What you will see in your terminal is a series of commits in the following format.

```{r}
p("img/git-log.PNG")
```

Each commit has a commit hash, the user who made the commit, the time of the commit, and the commit message. The name of the branch, the commit hash, and the commit message are denoted in the above figure.


### GitHub

We can also see a log of our commits in Github. This can be done as follows:

1. From the homepage of your Git repository on Github, click on the "Commits" tab:

```{r}
p("img/commit-navigation.PNG")
```

2. Now we can see the history of commits, in the following format:

```{r}
p("img/github-commits.PNG")
```

3. To view a commit in more detail, click on the commit message. Now you will see how that commit modified the files in our repository. The lines highlighted in red denotes what was removed, and lines highlighted in green show what was added:

```{r}
p("img/github-diffs.PNG")
```


## `git diff`

The `diff` command allows you to see local changes you have made, but not yet committed, to your repository.

### Command Line

To see your local changes:

1. Navigate to desired directory:

```bash
$ cd ~/cmu/76270/project4/github-instructions/
```

2. To view local changes:

```bash
$ git diff
```

Now observe your local changes to this repository. The file name is highlighted in the following figure. Meanwhile, lines with red text show the contents of the file that were deleted while lines with green text show the added content since your last commit.

```{r}
p("img/git-diff.PNG")
```

While you are in `diff`, you may hit the Enter or Return key to see more lines of differences. You may also hit Q to exit.


