# Setting Up Git Repositories (Elias) {#setting-up-repos}

## `git init`

The `init` command creates an empty git repository -- a `.git` directory containing everything you need for version control in this repository.

### Command Line {-}

To initialize a repository from the command line:

1. Navigate to desired parent directory:
  - *This directory will contain the git repository.*

```bash
$ cd ~/cmu/76270/project4/
```

2. Create a directory for your repository:

```bash
$ mkdir github-instructions
```

3. Navigate to new directory:

```bash
$ cd github-instructions
```

4. Initialize the repository:

```bash
$ git init
```

### GitHub {-}

On `github.com`, the `init` command is run automatically when a repository is created. Ensure that you are logged in before following these steps:

1. Navigate to home page:
  - [`http://github.com`](http://github.com)

2. Click on the green **New** button on the top-left of the page:

```{r}
p("img/new-repository.png")
```

3. Enter a name for the repository:
   - *The name of the repository must be unique to your user -- that is, you cannot give two repositories the same name.*

4. Enter additional customizations:
  - _You can include an optional description to provide more information about the purpose of the repository._
  - _Repositories can be public (others can view and use your code), or private (only you and invited users can access the repository)._
  - _`README.md`, `.gitignore`, and `LICENSE` are typical files to include in a repository. They are addressed in a later section._

```{r}
p("img/create-repository.png")
```

5. Click on **Create Repository** to complete.
   - _The page will be redirected to the empty repositories home page._

6. Finally, set up the repository:
   - _You can create a new repository on the command line by running:_

```bash
echo "# github-instructions" >> README.md
git init
git add README.md
git commit -m "first commit"
git remote add origin git@github.com:reroche/github-instructions.git
git push -u origin master
```

  - _Or you can import an existing repository on your computer into this GitHub new repository by running:_

```bash
git remote add origin git@github.com:reroche/github-instructions.git
git push -u origin master
```

## `git clone`

The `clone` command creates a copy of a of a repository into a newly created directory.

All repositories on GitHub have a unique URL, in the format:

> `https://github.com/`_username_`/`_repository-name_`.git`

The repository for this instructions, for example, is available at [`https://github.com/reroche/github-instructions`](https://github.com/reroche/github-instructions).

### Command Line {-}

To clone a repository from the command line:

1. Navigate to the desired parent directory.

```bash
$ cd ~/cmu/76270/project4/
```

2. Clone the repository using its GitHub URL:
   - _The new repository will be in a directory with its original name (e.g._ `github-instructions`).

```bash
$ git clone https://github.com/reroche/github-instructions.git
```

### GitHub {-}

The online interface allows you to easily browse and copy repository URLs to clone via the command line.

To clone or download a repository from Github:

1. Navigate to the repository URL:

> `https://github.com/reactjs/reactjs.org`

2. Click the green "Clone or Download" button:

```{r}
p("img/clone-repository.png")
```

3. Copy the link and clone from the command line, or download ZIP file.

## Forking on GitHub

Forking is copying a repository that belongs to another user into your repositories, granting you ownership permissions over that repository.

Forking cannot be done via the command line.

To fork a repository on Github, simply click the "Fork" button on the top right of a repository's home page.

```{r}
p("img/fork-repository.png")
```

