# Making Changes (Kylee) {#making-changes}

When making changes to a repository, generally a combination of `git add`, `git commit`, and `git status` will be used. The high level procedure for making changes is the following:

  1. Make edits to files in the repository.

  2. Add edited files to the staging area.

  3. Check which files have been staged/unstaged.

  4. Save these changes in a commit.

## `git add`

The `add` command allows users to add files to the staging area (Step 2). This essentially lets Git know that you made changes to the file and you would like to save them.

However, using the `add` command does not actually save the changes yet. That functionality is done by `git commit`.

### Command Line

(1) Adding files individually _(NOTE: If you include multiple files, they must be separated by a space.)_
```bash
$ git add README.md draft.Rmd
```


(2) Adding all tracked and untracked files (new, modified, and deleted)
```bash
$ git add -A
```

Tracked files are files that are included in the remote git repository. So, if you make changes to any of those files, they are already tracked.

However, if you create new files locally in the root directory, these files are untracked. Since you just created them, git does not track them since they are not yet in the remote git repository.


## `git commit`

The `commit` command actually saves any changes to files you made. In conjunction with `git add`, the `commit` command will save all files that you have previously added to the staging area.

Each commit is a snapshot, or a saved state, of your repository. Commits also require messages or captions to go along with them, usually describing the kinds of changes made.

This is beneficial if later on you are looking at all of your previous commits and want to see what changes you made in each one. Because these commit messages are so useful, there are two ways to write them.

### Command Line

(1) One-line commit message
```bash
$ git commit -m "Update add, commit, status sections in draft"
```


(2) Multi-line commit message
```bash
$ git commit
```

```{r}
p("img/git-commit.png")
```

## `git status`

The `status` command allows you to display any changes you have made to the directory you are currently working in. It details which changes have been staged (using `git add`), which changes have not, and which files are not being tracked by Git.

Essentially, you will be able to see which files Git will save if you were to commit. This allows you to first, see which files you have changed, and second, confirm all the files you want/don't want to track.


### Workflow

Going back to the high level procedure of how to make changes, here is an example of how to use these commands in conjunction.

Suppose I am working on a repository called `github-instructions` and I have just made changes to `README.md` and `draft.Rmd`, deleted a few image files, and also added new image files.

Using `git status` gives me a summary of the files I have changed, and further `git add` can move these changes to the staging area to be committed.

Using `git status` once again will now display an updates summary displayed that the files are now in the staging area. Finally, I can save these changes with a one-line commit message.

```{r}
p("img/git-workflow.png")
```

And just like that, we have successfully saved changes to our repository!


